Visualizations for the manuscript

### 2022-03-15 metanalysis_visualization/manuscript_Figures.Rmd
count plots added

>>>>

### Total counts with psychiatric conditions and total counts per month

#### At site level
```{r}
library(reshape2)

counts <- patient_count_psy_period_psy_all %>%
  mutate( total_cases = count_no_psy_patients + count_psy_patients) %>%
  select( siteid, time_p, time, month_year, count_psy_patients, total_cases)

counts2 <- reshape2::melt(counts ,  id.vars = c('siteid', 'time_p', 'time','month_year'), variable.name = 'group')
counts2$group <- gsub("count_psy_patients", "patients with psychiatric conditions", counts2$group )
counts2$group <- gsub("total_cases", "total number of patients", counts2$group )

counts2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  facet_wrap2("siteid", axes = "all", scales ="free") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
```

#### All together
```{r}
counts_agg <- patient_count_psy_period_psy_all %>%
  group_by( time_p ) %>%
  mutate( psy_cases = sum( count_psy_patients), 
    total_cases = sum(count_no_psy_patients) + sum(count_psy_patients)) %>%
  select( time_p, time, month_year, psy_cases, total_cases)

counts_agg2 <- reshape2::melt(counts_agg ,  id.vars = c('time_p', 'time','month_year'), variable.name = 'group')
counts_agg2$group <- gsub("count_psy_patients", "patients with psychiatric conditions", counts_agg2$group )
counts_agg2$group <- gsub("total_cases", "total number of patients", counts_agg2$group )

counts_agg2 %>% ggplot( aes( x= as.Date( time_p ), y = value, group= group )) +
  geom_point( aes( shape= group, color = group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "number of patients")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
```
